\documentclass[10pt,times]{article}
\include{Preamble}
\pagecolor[rgb]{0.6,0.6,0.6} %black
\begin{document}



\begin{enumerate}
    \item $n$ denotes the layer number, core
    \item In Figure~2A on each layer we currently write  $1$, $\cdots$, $N$. We should instead write $n=1$, $n=2$,  $\cdots$, $n=N$. 
    \item $^{n-1}\!{r}^{{}^{n}\!{m_{i}}+2}$
    \item $\text{pow}(^{n-1}\!{r},{{}^{n}\!{m_{i}}+2})$
    \item $I=(1,2,3)$, 
    \item $J=(1,2,3,4)$. 
\end{enumerate}

\subsection{Question and comments for HK}
\begin{enumerate}
    \item I think I should go back to the papers that talk about the effective properties of nacre. I think this is there in Currey's comprehensive paper.
    \item We could not come up with an effective non-dimensio
\end{enumerate}

\subsection{Question and comments for WF}
\begin{enumerate}
    \item It appears to me that the basis $\u{f}_i$ are not derived as $\u{f}_i \neq \u{x},_{i} $, when using the helical co-ordinate in the file HelicalFEA.pdf. (The coordiniates in that file are the only ones that HK has come accross in papers, and even in a recent paper in PRL.)
    \item However, we need to to clarify what $\varphi$. For each give $\varphi$ there does exist a helix. The question is what is the description of that helix. We clarify this in the manuscript. And finally, comment that the pitch of this helix changes from decreases from the outside to the inside.
    \item In the new version of the Fig. 2A, are we going to have single layer, or just a complete cylinder showing internal structure. (I am leaning towards shoing a single layer. ) 
\end{enumerate}








\end{document}